Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-02-05 ms.tex
added figure for OTIS fringing
showing evidence for fringing in CV3 data

The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec}, probably because of the broad PSF.
However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
\textcolor{red}{\bf Is this fringing?}

@@

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{fringing_grism_otis.pdf}
\caption{The average OTIS spectrum over the time series grism test shows evidence for fringing.
An illustrative sinusoidal function is plotted for comparison.
}\label{fig:avgOtisGrismSpecFringing}
\end{figure}

The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec} and is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
\textcolor{red}{\bf Is this fringing?}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing.
An illustrative sinusoidal function is plotted for comparison.
}\label{fig:CV3GrismSpecFringing}
\end{figure}
